Finite-state morphological transducers for three Kypchak languages

### 2014-03-22 kipchak-lrec-2013/kipchak-paper.tex
яхшы example ;)
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@51062 72bbbca6-d526-0410-a7d9-f06f51895060

Most of the stems in the lexicon can be used, with no extra suffixes in any of these functions, for 
example the adjective жақсы in Kazakh can be used as attributively, жақсы кітап `good book', adverbially
жақсы ойнадыңыз `(you) played well', and substantively (as a noun) `жақсы келетін еді' `(the) good (ones) would come'. This
is a productive process and relevant to the morphotactics, as an adjective used substantively may take the 
full range of case and possessive suffixes, and adjectives used adverbially will take a different set of 
clitics than adjectives used substantively and attributively.

@@

Types of these phenomena include characters used to represent multiple phonological forms, loanwords, and acronyms and numerals.  A brief overview of each follows, along with examples and details of our solution.

>>>>

Most of the stems in the lexicon can be used, with no extra suffixes in any of these functions, for 
example the adjective ‹яхшы› in Tatar can be used as attributively (e.g., ‹яхшы аучы› `good hunter'), adverbially
(e.g., ‹яхшы бөгелә› `bends well'), and substantively, i.e. as a noun (e.g., ‹яхшы белән› `with a good [person]’). This
is a productive process and relevant to the morphotactics, as an adjective used substantively may take the 
full range of case and possessive suffixes, and adjectives used adverbially will take a different set of 
clitics than adjectives used substantively and attributively.

@@

Types of these phenomena include single characters used to represent multiple phonological forms, loanwords, and acronyms and numerals.  A brief overview of each follows, along with examples and details of our solution.
